The Exoplanet Orbit Database 2, 2014 updates

### 2014-03-10 draft/ms.tex
Tiny revisions in Sec 2 and ref.

{\bf LAMBDA} is the projected spin-orbit misalignment ($\lambda$) in
the unit of degree. We report the projected spin-orbit misalignment of
transiting systems, which is measured by, e.g., the Rossiter-McLaughlin
effect or planet transiting star spots ZZZ add references for RM effect and the star spot method. $\lambda$ is introduced because the true spin-orbit angle
($\phi$), defined as the angle between the stellar spin axis and the
orbital axis, is normally not directly measurable. We follow the
definition of $\lambda$ in \cite{Fabrycky2009} where the
coordinates are defined as follows; the $z$-axis points toward the
observer, the $x$-axis points along the intersection of the sky plane
and the planet's orbital plane with the ascending node of the planet
having $x<0$, and the $y$-axis completes a right
handed-triad. $\lambda$ is measured clockwise on the sky from the
$y$-axis to the projected stellar rotational axis. $\lambda$ is not a newly added field but we describe it here because $\lambda$'s were not reported consistently since some literatures
report $\beta = -\lambda$ instead. We sorted these cases out and made
sure that our $\lambda$'s are following the definition of \cite{Fabrycky2009}.
%------------------------------------------------------------------------------
\subsection{Transit Parameters}\label{sec:transit}

>>>>

{\bf LAMBDA} is the projected spin-orbit misalignment ($\lambda$) in
the unit of degree. We report the projected spin-orbit misalignment of
transiting systems, which is measured by, e.g., the
Rossiter-McLaughlin effect or planet transiting star spots ZZZ add
references for RM effect and the star spot method. $\lambda$ is
introduced because the true spin-orbit angle ($\phi$), defined as the
angle between the stellar spin axis and the orbital axis, is normally
not directly measurable. We follow the definition of $\lambda$ in
\cite{Fabrycky2009} where the coordinates are defined as follows; the
$z$-axis points toward the observer, the $x$-axis points along the
intersection of the sky plane and the planet's orbital plane with the
ascending node of the planet having $x<0$, and the $y$-axis completes
a right handed-triad. $\lambda$ is measured clockwise on the sky from
the $y$-axis to the projected stellar rotational axis. $\lambda$ is
not a newly added field but we describe it here because $\lambda$'s
were not reported consistently since some literatures report $\beta =
-\lambda$ instead. We sorted these cases out and made sure that our
$\lambda$'s are following the definition of \cite{Fabrycky2009}.

%------------------------------------------------------------------------------
\subsection{Transit Parameters}\label{sec:transit}
